### 2014-05-15 latex/phd_thesis.tex
Began section on parameter estimation.

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\

>>>>

bp & base pair \\
kb & kilobase = $1000$ bp \\
Mb & megabase = $1,000,000$ bp \\
Gb & gigabase = $1,000,000,000$ bp \\
WGBS & whole genome bisulfite sequencing \\
RRBS & reduced representation bisulfite sequencing \\
FDR & false discovery rate \\
DMR & differentially methylated region \\
DMC & differentially methylated cytosine \\
HMM & hidden Markov model \\
CNV & copy number variant \\
SE & single-end sequencing \\
PE & paired-end sequencing \\
